---
title: "stats510_1"
author: "Christoper Chan"
date: "December 1, 2018"
output: 
  github_document:
    pandoc_arg: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1.1 Overview

* AR(1) model: $x_{t} = \delta + \phi_{1}x_{t-1} + w_{t}$
    + Same properties of linear regression


##1.2 Sample ACF and Properities of AR(1) Model

* Weakly stationary series requirements:
    1. Mean $E(x_{t})$ is same for all _t_
    2. Variance of $x_t$ is same for all _t_
    3. Corvariance and correlation between $x_t$ and $x_{t-h}$ is same for all _t_
* Autocorrelation function (ACF) = gives correlation between $x_t$ and $x_{t-h}$ for $h = 1, 2...n$
    + ACF = $\frac{Cov(x_t, x_{t-h})}{s(x_t)s(x_t)} = \frac{Cov(x_t, x_{t-h})}{Var(x_t)}$
* Properties of AR(1) model:
    + Mean($\mu$) = $\frac{\delta}{1-\phi_1}$
    + Var($x_t$) = $\frac{\sigma^2_w}{1-\phi^2_1}$
    + Cor($\rho_h$) = $\phi^2_1$
* Create stationary series by first differences ($y_t = x_t - x_{t-1}$)


##1.3 Coded Examples
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(forecast)
```

```{r}
my_quakes <- scan('data/quakes.txt')
head(my_quakes)
quakes = ts(my_quakes)
```

Honestly, I've looked around for ways to plot this in ggplot2 and I'm just not sure. Because there is no X component of dataset quakes, I'm not sure how 
```{r}
plot(quakes, type='b')
```

```{r}
lag.plot(quakes, lags=1, do.lines=F)
```

```{r}
acf(quakes, xlim=c(1,20))
```

Regression of quakes$x and created variable of lag_1
```{r}
quakes_lag1 <- lag(my_quakes, 1)

y = cbind(my_quakes, quakes_lag1)
ar1_lr <- lm(y[,1]~y[,2])
summary(ar1_lr)
```















